Spatiotemporal Data Classification

### 2017-12-28 Report/BigDataHomework1.tex
update report
changes to report

	\tableofcontents
    \newpage
	\listoffigures
	\newpage

@@

	\subsection{Question A1}
	For this part a test file is given (test\_set\_a1.csv) containing additional trips. For each of these trips, the k nearest neighbours are targeted (in this exercise k=5) and an image file is produced, showing all six trips (the test trip and the trips from the training file) on six different maps. Under each map, the neighbour index, the journey\_id, the dynamic time warping and the time needed to process this neighbour in millisec.

	The code for this question is in the file NearestNeighbours.py. Firstly, all test trips in the test file are extracted and stored in the same data structure as the trip list that contains the training dataset. Subsequently, for each test trip all nearest neighbours are calculated in the function find\_nearest\_neighbours\_for\_test\_trip, keeping the time needed in a variable. For the test trip and all the training trips, the longitudes and latitudes are stored in tuples which are provided to the function calculate\_dynamic\_time\_warping in order to find the distance between two points. The calculated distances are stored in a list, which finally is sorted in ascending order and only the five nearest neighbours are kept.

	Since now the nearest neighbour trips are found, the trips list is updated (function: get\_updated\_trips\_list) containing now only those five trips. The final step now is to visualize the six trips. For this purpose, three list are created: a list with all the points (longitudes and latitudes), a list with the labels and a list with the colors (in this question the only color is the blue). All this data is provided to the function visualize\_paths in the utils.py file.

	In order to be able to create an image containing all the six maps each time, the rasterize.js file is required. In this function, both .html and .jpg files are created. Their names are kept in a list and when the final image file is created these files are deleted. 
	\todo{describe how the visualization function works}

@@

	\subsection{Question A2}
	Following the same logic as above, the given test file(test\_set\_a2.csv) is parsed and the data are stored in the usual format and the function find\_similar\_subroots\_per\_test\_trip is used to determine the nearest sub-routes for each test trip.

	The points are stored as tuples, similarly to the above question, both for the test and the training datasets, and the function datetime.datetime.now() is used so as to calculate the start and end time of each nearest subroute trip processing. The latest is performed in the method calc\_lcss.
	\todo{describe calc and update lcss}

>>>>

	\tableofcontents
    \newpage
	\listoffigures
	\newpage
	\listoftodos
	\newpage

@@

	\subsection{Question A1}
	For this part a test file is given (test\_set\_a1.csv) containing additional trips. For each of these trips, the k nearest neighbours are targeted (in this exercise k=5) and an image file is produced, showing all six trips (the test trip and the trips from the training file) on six different maps. Under each map, the neighbour index, the journey\_id, the dynamic time warping and the time needed to process the neighbours of this test trip in millisec.

	The code for this question is in the file NearestNeighbours.py. Firstly, all test trips in the test file are extracted and stored in the same data structure as the trip list that contains the training dataset. Subsequently, for each test trip all nearest neighbours are calculated in the function find\_nearest\_neighbours\_for\_test\_trip, keeping the time needed in a variable. At the beginning of the trips processing, the tic method from utils.py file is used (finds the current time in millisec using the datetime.datetime.now() method). After having found the nearest neighbours for the given test trip, the method tictoc() is called, returning the required time. In order to find the nearest neighbours, the following process is implemented: For the test trip and all the training trips, the longitudes and latitudes are stored in tuples which are provided to the function calculate\_dynamic\_time\_warping in order to find the distance between two points. The calculated distances are stored in a list, which finally is sorted in ascending order and only the five nearest neighbours are kept.

	Since now the nearest neighbour trips are found, the trips list is updated (function: get\_updated\_trips\_list) containing now only those five trips. The final step now is to visualize the six trips. For this purpose, three list are created: a list with all the points (longitudes and latitudes), a list with the labels and a list with the colors (in this question the only color is the blue). All this data is provided to the function visualize\_paths in the utils.py file in order to export the trips as map images.

	In order to be able to create an image containing all the six maps each time, the rasterize.js file is required as well as phantomjs. In this function, both .html and .jpg files are created. First of all, the function write\_group\_gml is used so as to create the html files (this function is described above in question c). These html files are converted to images using the function html\_to\_png. File names are kept in a list and when the final image file is created (containing all six maps) these files are deleted. Afterwards, images as displayed as collection of plots and exported in the .jpg format.

@@

	\subsection{Question A2}
	Following the same logic as above, the given test file(test\_set\_a2.csv) is parsed storing the data in the usual format and the function find\_similar\_subroots\_per\_test\_trip is used to determine the nearest sub-routes for each test trip.

	Similarly to the above question, the points are stored as tuples and the required time is calculated using the relevant methods from the utils.py file. To begin with, the method calc\_lcss is called
	\todo{describe calc and update lcss}
